Interval Probability and Measurement for Fuzzy Quantum Theories

### 2016-11-15 prob.tex
prob.tex \section{Proofs} Keep typing...

% \makeatletter
% \newtheoremstyle{indented}
%   {3pt}% space before
%   {3pt}% space after
%   {\addtolength{\@totalleftmargin}{3.5em}
%    \addtolength{\linewidth}{-3.5em}
%    \parshape 1 3.5em \linewidth}% body font
%   {}% indent
%   {\bfseries}% header font
%   {.}% punctuation
%   {.5em}% after theorem header
%   {}% header specification (empty for default)
% \makeatother
% \theoremstyle{indented}
\theoremstyle{remark}
\newtheorem{example}{Example}
\newtheorem{definition}{Definition}
\newtheorem{cor}{Corollary}
\newtheorem{lemma}{Lemma}
\newtheorem{thm}{Theorem}
\newtheorem{case}{Case}
\newtheorem{conjecture}{Conjecture}
\newtheorem{problem}{Problem}
\newcommand{\events}{\ensuremath{\mathcal{E}}}
\newcommand{\qevents}{\ensuremath{\mathcal{E}}}
\newcommand{\pmeas}{\ensuremath{\mu}}
\newcommand{\Hilb}{\mathcal{H}}
\newcommand{\ps}{\texttt{+}}
\newcommand{\ms}{\texttt{-}}
\newcommand{\poss}{{\mbox{\wesa{possible}}}}
\newcommand{\imposs}{{\mbox{\wesa{impossible}}}}
\newcommand{\likely}{{\mbox{\wesa{likely}}}}
\newcommand{\unlikely}{{\mbox{\wesa{unlikely}}}}
\newcommand{\necess}{{\mbox{\wesa{certain}}}}
\newcommand{\overflow}{{\mbox{\wesa{overflow}}}}
\newcommand{\unknown}{{\mbox{\wesa{unknown}}}}

@@

>>>>

% \makeatletter
% \newtheoremstyle{indented}
%   {3pt}% space before
%   {3pt}% space after
%   {\addtolength{\@totalleftmargin}{3.5em}
%    \addtolength{\linewidth}{-3.5em}
%    \parshape 1 3.5em \linewidth}% body font
%   {}% indent
%   {\bfseries}% header font
%   {.}% punctuation
%   {.5em}% after theorem header
%   {}% header specification (empty for default)
% \makeatother
% \theoremstyle{indented}
\theoremstyle{remark}
\newtheorem{example}{Example}
\newtheorem{definition}{Definition}
\newtheorem{cor}{Corollary}
\newtheorem{lemma}{Lemma}
\newtheorem{thm}{Theorem}
\newtheorem{case}{Case}
\newtheorem{conjecture}{Conjecture}
\newtheorem{problem}{Problem}
\newtheorem{claim}{Claim}
\newcommand{\events}{\ensuremath{\mathcal{E}}}
\newcommand{\qevents}{\ensuremath{\mathcal{E}}}
\newcommand{\pmeas}{\ensuremath{\mu}}
\newcommand{\Hilb}{\mathcal{H}}
\newcommand{\ps}{\texttt{+}}
\newcommand{\ms}{\texttt{-}}
\newcommand{\poss}{{\mbox{\wesa{possible}}}}
\newcommand{\imposs}{{\mbox{\wesa{impossible}}}}
\newcommand{\likely}{{\mbox{\wesa{likely}}}}
\newcommand{\unlikely}{{\mbox{\wesa{unlikely}}}}
\newcommand{\necess}{{\mbox{\wesa{certain}}}}
\newcommand{\overflow}{{\mbox{\wesa{overflow}}}}
\newcommand{\unknown}{{\mbox{\wesa{unknown}}}}

@@

\begin{thm}\label{thm:analogTheorem3.5Gleason1957}~
\begin{itemize}
\item Let $f:\mathbb{C}S^{2}\rightarrow\mathbb{R}$ be a bounded continuous
approximation frame function of weight~$\left(W_{l},W_{r}\right)$,
$W=\frac{W_{l}+W_{r}}{2}$. Recall $f$ could be uniquely extended
to the whole space~$\mathbb{C}^{3}$ by $f\left(0\right)=0$ and
$f\left(\ket{\psi}\right)=\left\Vert \ket{\psi}\right\Vert ^{2}f\left(\left\Vert \ket{\psi}\right\Vert ^{-1}\ket{\psi}\right)$
for nonzero vector~$\ket{\psi}$.
\end{itemize}
Then, $\left|Q\left(\ket{\psi}\right)-f\left(\ket{\psi}\right)\right|\le27\delta\left(W_{r}-W_{l},W_{r}-W_{l},\omega_{f}\right)+27\delta\left(W_{r}-W_{l},W_{r}-W_{l},\omega_{f'}\right)+18\left(W_{r}-W_{l}\right)$
for all $\ket{\psi}\in\mathbb{C}S^{2}$.\qed\end{thm}
\begin{proof}
This proof will be separated into two parts. The first part will estimate
the error between the approximation frame function and the quadratic
form on every complex two-space. The second part will then verify
the quadratic forms in the first part could be connected and get a
quadratic form on the whole space.

\begin{claim}For any pair of vectors~$\ket{\psi_{0}},\ket{\psi_{1}}\in\mathbb{C}S^{2}$. 
\begin{itemize}
\item Consider the complex vector space spanned by $\ket{\psi_{0}}$ and
$\ket{\psi_{1}}$, and $\mathbb{C}S^{1}$ be its unit sphere, i.e.,
\[
\left\{ \alpha_{0}\ket{\psi_{0}}+\alpha_{1}\ket{\psi_{1}}\middle|\alpha_{0},\alpha_{1}\in\mathbb{C}\textrm{ and }\left|\alpha_{0}\right|^{2}+\left|\alpha_{1}\right|^{2}=1\right\} \textrm{ .}
\]
\item $M=\max_{\ket{\psi}\in\mathbb{C}S^{1}}f\left(\ket{\psi}\right)=f\left(\ket{0}\right)$.
\item $\ket{1}\in\mathbb{C}S^{1}$ is orthogonal to $\ket{0}$.
\item $Q\left(\ket{\psi}\right)=M\ip{0}{\psi}^{2}+\left(W-M\right)\ip{1}{\psi}^{2}$.
\item $f'\left(\ket{\psi}\right)=f\left(\ket{\psi}\right)-Q\left(\ket{\psi}\right)$.
\item $\delta\left(\eta,W_{\Delta},\omega_{f}\right)=\sup_{\theta\in\left[0,\frac{\pi}{2}\right)}\min\left\{ \min_{n\ge n\left(\theta\right)}2n\eta+4nW_{\Delta}+2\omega_{f}\left(2-2\cos\left(\frac{\pi^{2}}{n}\right)\right),2\omega_{f}\left(2\cos\theta\right)\right\} $.
\end{itemize}
Then, $\left|Q\left(\ket{\psi}\right)-f\left(\ket{\psi}\right)\right|\le27\delta\left(W_{r}-W_{l},W_{r}-W_{l},\omega_{f}\right)+27\delta\left(W_{r}-W_{l},W_{r}-W_{l},\omega_{f'}\right)+18\left(W_{r}-W_{l}\right)$
for all $\ket{\psi}\in\mathbb{C}S^{1}$.\qed\end{claim}
\begin{proof}
For all $\ket{\psi}\in\mathbb{C}S^{1}$, 
\begin{eqnarray*}
 &  & \left|Q\left(\ket{\psi}\right)-f\left(\ket{\psi}\right)\right|\\
 & = & \left|Q\left(\ket{\psi}\right)-f\left(\ket{0}\ip{0}{\psi}+\ket{1}\ip{1}{\psi}\right)\right|\\
 & = & \left|Q\left(\frac{\left|\ip{0}{\psi}\right|}{\ip{0}{\psi}}\ket{\psi}\right)-f\left(\frac{\left|\ip{0}{\psi}\right|}{\ip{0}{\psi}}\left(\ket{0}\ip{0}{\psi}+\ket{1}\ip{1}{\psi}\right)\right)\right|\\
 & = & \left|Q\left(\frac{\left|\ip{0}{\psi}\right|}{\ip{0}{\psi}}\ket{\psi}\right)-f\left(\ket{0}\left|\ip{0}{\psi}\right|+\ket{1}\frac{\left|\ip{0}{\psi}\right|}{\ip{0}{\psi}}\frac{\ip{1}{\psi}}{\left|\ip{1}{\psi}\right|}\left|\ip{1}{\psi}\right|\right)\right|\\
 & \le & 27\delta\left(W_{r}-W_{l},W_{r}-W_{l},\omega_{f}\right)+27\delta\left(W_{r}-W_{l},W_{r}-W_{l},\omega_{f'}\right)+18\left(W_{r}-W_{l}\right)
\end{eqnarray*}
where the last inequality holds because $\ket{1}\frac{\left|\ip{0}{\psi}\right|}{\ip{0}{\psi}}\frac{\ip{1}{\psi}}{\left|\ip{1}{\psi}\right|}\in\mathbb{C}S^{1}$
is orthogonal to $\ket{0}$, $\bra{0}\left(\frac{\left|\ip{0}{\psi}\right|}{\ip{0}{\psi}}\ket{\psi}\right)=1\in\mathbb{R}$,
and 
\[
\left(\ket{1}\frac{\left|\ip{0}{\psi}\right|}{\ip{0}{\psi}}\frac{\ip{1}{\psi}}{\left|\ip{1}{\psi}\right|}\right)^{\dagger}\left(\frac{\left|\ip{0}{\psi}\right|}{\ip{0}{\psi}}\ket{\psi}\right)=\frac{\ip{\psi}{1}}{\left|\ip{\psi}{1}\right|}\frac{\left|\ip{\psi}{0}\right|}{\ip{\psi}{0}}\bra{1}\frac{\left|\ip{0}{\psi}\right|}{\ip{0}{\psi}}\ket{\psi}\in\mathbb{R}\textrm{ .}
\]
\end{proof}
\end{proof}
